---
title: "Project 2"
author: "Brian Bruxvoort"
date: "2023-11-14"
output: pdf_document
---

```{r}
crab <- read.table("Horseshoe.txt", header = TRUE)
head(crab)
```

```{r}
mod.fit <- glm(formula = satellite ~ width, data = crab, family = poisson(link = log))
summary(mod.fit)
```

# Part 1
Perform a Wald test for a Beta1

z = beta hat1/standard error = 0.16/0.1997 = 8.216
Width is significant.

# Part 2
How can we perform a LRT for an explanatory variable?
```{r, message=FALSE, warning=FALSE}
library(package = car)
Anova(mod = mod.fit, test = "LR")
```


# Part 3
How can we estimate the expected number of satellites when the shell width is 23?
```{r}
width <- 23
mod.predict <- predict(mod.fit, data.frame(width = 23))
mod.predict
```

# Part 4
How can we find a Wald confidence interval for mu? Are there any worries about interval limits being outside of the appropriate numerical range?
```{r}
conf.int <- confint(mod.fit)
conf.int
```

No there are no worries that the confidence interval for mu is not outside the limits because it is not below 0 or above 1.

# Part 5
How can we find a Profile LR confidence interval for mu?
```{r}
exp(confint(object = mod.fit, level = 0.95))
```

# Part 6
How could you estimate the covariance matrix and print it in R?
```{r}
vcov(mod.fit)
```

# Part 7
How could you include some type of transformation of an explanatory variable(s) in the model?
```{r}
mod.fit2 <- glm(formula = satellite ~ width + I(width^2), data = crab, family = poisson(link = log))
summary(mod.fit2)
```

